Estimation of the perceived time of presence of sources in urban acoustic environment using deep learning techniques

### 2019-06-04 paper/paperV1.tex
fix ref

To validate the use of simulated sound scenes with new scenarios as well as reduced source complexity in the development of prediction models, the perceptual space generated by the experiment's five general scales (pleasantness, liveliness, overall loudness, interest and calmness) is studied. It is obtained by performing a principal components analysis (PCA) on the corresponding perceptual responses averaged along participants. No standardization is applied to the data. Figure~\ref{fig:pspace_rec} and Figure~\ref{fig:pspace_sim} compare the results for scenes based on recordings (n=25) and new scenarios (n=75) respectively. The resulting spaces are similar, with only overall loudness and pleasantness axes slightly rotated between the two subcorpora. For both sets the variance explained by the first two components is similar, resp. 79.4\% - 18.1\% and 79.6\% - 15.2\%. Furthermore, these representations are comparable to those found in previous work on perceptual dimensions~\cite{axelsson2010, cain2013}. Thus, the use of simulated scenes based on both real and new scenarios does not result in major differences in the relations between perceptual quantities. Additionally, the assessments averaged on all subjects are projected onto the PCA space for each scene and represented in Figure~\ref{fig:pspace_p1} as red dots for simulated scenes corpus and blue dots for recorded and replicated scenes. The space covered by scenes based on new scenarios covers that of the studied real-life environments, further demonstrating the effectiveness of the scene generation procedure in terms of diversity of scenarios.

>>>>

To validate the use of simulated sound scenes with new scenarios as well as reduced source complexity in the development of prediction models, the perceptual space generated by the experiment's five general scales (pleasantness, liveliness, overall loudness, interest and calmness) is studied. It is obtained by performing a principal components analysis (PCA) on the corresponding perceptual responses averaged along participants. No standardization is applied to the data. Figure~\ref{fig:pspace_rec} and Figure~\ref{fig:pspace_sim} compare the results for scenes based on recordings (n=25) and new scenarios (n=75) respectively. The resulting spaces are similar, with only overall loudness and pleasantness axes slightly rotated between the two subcorpora. For both sets the variance explained by the first two components is similar, resp. 79.4\% - 18.1\% and 79.6\% - 15.2\%. Furthermore, these representations are comparable to those found in previous work on perceptual dimensions~\cite{axelsson2010, cain2013}. Thus, the use of simulated scenes based on both real and new scenarios does not result in major differences in the relations between perceptual quantities. Additionally, the assessments averaged on all subjects are projected onto the PCA space for each scene and represented in Figure~\ref{fig:pspace_rec} as red dots for simulated scenes corpus and blue dots for recorded and replicated scenes. The space covered by scenes based on new scenarios covers that of the studied real-life environments, further demonstrating the effectiveness of the scene generation procedure in terms of diversity of scenarios.
